An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-21 article.tex
Added figure, commented out bad table.

      \caption{Summary of models; their predictors, covariates and variable interactions.}
      \label{tab:tab1}

@@

($< 2.200E-16$, see Tables  and )

@@

@@

% \ref{tab:ftests}
% We need a table with all F-tests.
%         | Yield   | ...
% Model 1 | -2e^-16 | ...

@@

To determine if predictors significantly related to a Model's response variable, F-tests were conducted. Models 1 and 2 showed significant linear relationships present between all predictors and their response variables (see Table \ref{tab:ftests}). Predictors in Models 3 and 4 reported the same significance for each variable except for scope 1 emissions. Scope 1 emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients scope one emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yield and average price per tonne as a ratio to area harvested, respectively).

@@

>>>>

      \caption{Summary of models; their predictors, covariates and variable interactions.}\label{tab:tab1}

@@

($< 2.200E-16$, see Tables  and) 

@@

          \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\

@@

@@

% This table is absolutely trash.
% Kate madea good point that, although figures can be combined into a single figure. Tables cannot.
% cheat way to multi line comment
\iffalse{}
  \caption{Ftests and wsutff}\label{tab:ftests}
    \begin{tabular}{@{}cllllllll@{}}
       & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Scope 1\\ Emissions\end{tabular}}} & \textbf{Year} & \textbf{\begin{tabular}[c]{@{}l@{}}GI\\ Region\end{tabular}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ *\\ Scope 1\\ Emissions\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Area\\ Harvested\\ *\\ Water\\ Used\end{tabular}}} & \multicolumn{1}{c}{\textbf{\begin{tabular}[c]{@{}c@{}}Year\\ *\\ GI\\ Region\end{tabular}}} \\ \midrule
      \textbf{Model 1} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 3211 & 10.4 & 6.6 & 70.6 & 1507.1 &  &  &  \\
      F-Value & 34187.908 & 110.255 & 70.56 & 83.533 & 297.163 &  &  &  \\
      Pr(>F) & 2.20E-16 & 2.20E-16 & 2.20E-16 & 2.20E-16 & 2.20E-16 &  &  &  \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 2} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 2856.23 & 473.32 & 33.06 &  &  & 53.47 & 0.28 & 975.61 \\
      F-Value & 15363.1866 & 177.8109 & 2545.9357 &  &  & 287.6126 & 1.5097 & 12.3766 \\
      Pr(>F) & <2e-16 & <2e-16 & <2e-16 &  &  & <2e-16 & 0.2192 & <2e-16 \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 3} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 2142.46 & 0.32 & 0.04 & 13.24 & 649.83 &  &  &  \\
      F-Value & 84905.8197 & 12.5874 & 1.4915 & 87.4771 & 515.0601 &  &  &  \\
      Pr(>F) & <2.2E-016 & 0.0003947 & 0.2220844 & <2.2E-016 & <2.2E-016 &  &  &  \\
      \multicolumn{1}{l}{} &  &  &  &  &  &  &  &  \\
      \textbf{Model 4} &  &  &  &  &  &  &  &  \\
      \begin{tabular}[c]{@{}c@{}}Total Sum\\ of Squares\end{tabular} & 1868.46 & 274.92 & 0.04 &  &  & 35.02 & 4.18 & 582.96 \\
      F-Value & 44084.0278 & 6486.2867 & 0.8311 &  &  & 826.1925 & 98.5895 & 56.6019 \\
      Pr(>F) & <2e-16 & <2e-16 & 0.3621 &  &  & <2e-16 & <2e-16 & <2e-16
\fi
% model 1 - all sig
% model 2 - area * water used interaction was not sig
% model 3 - scope 1 was not sig
% model 4 - scope 1 was not sig
To determine if predictors significantly related to a Model's response variable, F-tests were conducted. Aside from 3 variables, all F-tests across each model indicated a significant contribution was made at 95\% confidence (See Table
%\ref{tab:ftests}).
). The exceptions were scope 1 emissions in models 3 and 4, as well as the interaction between area harvested and water used in Model 3. 
Models 1 and 2 showed significant linear relationships present between all predictors and their response variables (with P-values being less than 2.200E-16). Predictors in Models 3 and 4 reported the same significance for each variable except for scope 1 emissions. Scope 1 emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients scope 1 emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yield and average price per tonne as a ratio to area harvested, respectively).

@@

\includegraphics{violinplot.pdf}
